mathml: Translate R expressions to MathML and LaTeX

### 2023-01-29 rj/mathml.Rmd
checks passed
minor

```{r setup, include=FALSE}
# linear models: DepVar ~ X0 + X1

library(mathml)

@@

ntheta <- lapply(lapply(FUN=as.symbol, names(theta)), FUN=mathout,
    flags=list(cat=FALSE))
ttheta <- lapply(theta, FUN=mathout, flags=list(cat=FALSE))
tci <- lapply(ci, FUN=mathout, flags=list(cat=FALSE))

>>>>

```{r setup, include=FALSE}
library(mathml)

@@

ntheta <- lapply(lapply(FUN=as.symbol, names(theta)), FUN=mathout,
    flags=list(cat=FALSE))
ttheta <- lapply(theta, FUN=mathout, flags=list(cat=FALSE))
tci <- lapply(ci, FUN=mathout, flags=list(cat=FALSE, sep=","))
